RCloud: Integrating Exploratory Visualization, Analysis and Deployment

### 2014-03-14 paper.tex
yes

There has been considerable work on specific techniques such as
social bookmarking \cite{Millen:2006:DSB} \cite{Heer:2007:VAV}
to support collaborative or social 
Our goal is to provide a productive environment in which such
techniques may be integrated and made available to a community.
Similarly, there are computational methods to support
high performance execution in an incremental code development
environment \cite{Guo:2010:TPI}.

@@

Our work has been inspired by and has benefited from other recent projects
to improve data analysis environments and processes, including RStudio,
R packages such as Markdown, knitr and Shiny \cite{CRAN}, and iPython notebooks,
to name a few. RStudio aims at providing an integrated development environment
for R programming, with support for publishing code in packages. Markdown,
knitR and Shiny provide R with sophisticated reporting capabilities, including
interactive web interfaces. IPython \cite{Perez:2007:IAS}
shares many of our goals...

>>>>

There has been notable work on specific techniques such as
social bookmarking \cite{Millen:2006:DSB} \cite{Heer:2007:VAV}
and crowdsourcing \cite{Fast:2014:ECS} to support collaborative
or social development or analysis processes.
Similarly, there are computational methods to support high
performance execution in incremental code development
environments \cite{Guo:2010:TPI}.
Our goal is to define an environment in which many such
techniques may be integrated and made available to a broad community.

@@

Our work has been inspired by and has benefited from other recent projects
to improve data analysis environments and processes, including RStudio,
R packages such as Markdown, knitr and Shiny \cite{CRAN}, and iPython notebooks,
to name a few. RStudio aims at providing an integrated development environment
for R programming, with support for publishing code in packages. Markdown,
knitR and Shiny provide R with sophisticated reporting capabilities, including
interactive web interfaces. IPython \cite{Perez:2007:IAS}
shares many of our goals, such as providing a comprehensive environment
for analysis and programming, with sharable documents on the web.
